% Created 2020-07-18 Sa 16:59
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Liam Hurwitz}
\date{\today}
\title{Test Protokol}
\hypersetup{
 pdfauthor={Liam Hurwitz},
 pdftitle={Test Protokol},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section{Testfall Single Player}
\label{sec:orgc5dc561}
\begin{enumerate}
\item Login Screen
\begin{enumerate}
\item Register
\begin{itemize}
\item Test if name exists
\item Test if one can register
\item Does the Client alert if the Server is offline?
\end{itemize}
\item Login
\end{enumerate}
\item Menu Screen
\begin{enumerate}
\item New Game
\begin{itemize}
\item Single Player
\begin{itemize}
\item Goes back to Fight Screen
\item Goes back to Station Map
\item Goes back to Shop
\end{itemize}
\end{itemize}
\item Single Player (Ship Select Screen)
\begin{itemize}
\item Are the Stats Updated for the Ship?
\item Can I spawn into the Map?
\item Are there Any Exceptions?
\end{itemize}
\end{enumerate}
\end{enumerate}

\section{Station Screen}
\label{sec:orga891bce}
\begin{enumerate}
\item StationMap
\begin{enumerate}
\item Select Planet
\begin{itemize}
\item Can I select every Planet?
\item Does the Dialog Appear?
\end{itemize}
\item Jump
\begin{itemize}
\item Jump can I jump to every Planet?
\item Do I see if I have visited the Planet?
\item Does the Back Button work?
\end{itemize}
\end{enumerate}
\end{enumerate}

\section{Stop Abstract}
\label{sec:org3bde3ec}
\begin{enumerate}
\item StopScreen
\begin{enumerate}
\item Leave
\begin{enumerate}
\item Leave
\item View Map -> Station Map
\end{enumerate}
\item Explore
\begin{enumerate}
\item Flee -> Station Screen
\item Fight -> CombatScreen
\item Shop -> Station Mao
\end{enumerate}
\item Back to Map -> Station Map
\end{enumerate}
\end{enumerate}

\section{Combat Screen}
\label{sec:org9c941a6}





\section{Strangenes}
\label{sec:org4b85c14}
\begin{itemize}
\item Rainbow Line
\item Pruebe Kopf in ShipSelectScreen
\item Bug Ship is not add at Stop
\item Jump to same Planet
\end{itemize}
\end{document}
